%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Digital Signal Processing Software Engineer Intern} % Job title
    {Coherent Logix} % Organization
    {MATLAB, C, Assembly} % Location
    {May 2023 - Aug 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented receiver algorithms for wireless 802.11b protocol on custom DSP processors using C and Assembly, with MATLAB prototype code as reference.}
        \item {Introduced optimizations to existing algorithm implementation, reducing overall runtime by 25\% and successfully meeting the allotted speed requirement.}
        \item {Documented convoluted assembly code blocks thoroughly by adding equivalent C code as comments and including explanations of any optimization tricks.}
      \end{cvitems}
    }

  \cventry
    {DevOps Intern} % Job title
    {Sony Interactive Entertainment} % Organization
    {AWS, Kubernetes, Jenkins} % Location
    {Sep 2022 - Dec 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Deployed \boldstyle{Promtail/Loki/Grafana} logging stack using \boldstyle{Helm} to aggregate logs from 100+ \boldstyle{Kubernetes} pods, increasing log accessibility and transparency across development teams.}
        \item {Wrote Python script with Slack integration to periodically report and clean unused AWS volumes in order to reduce tech debt and cut AWS costs.}
        \item {Automated the deletion of vulnerable security groups and sent relevant email alerts using AWS \boldstyle{Lambda, SNS, and EventBridge} in order to remediate common security issues.}
        % \item {Implemented system to alert team on insecure security group creation using AWS Lambda, SNS, and EventBridge.}
        \item {Performed \boldstyle{time-sensitive} Jenkins server operations during maintenance windows.}
      \end{cvitems}
    }

  \cventry
    {Front End Software Developer Intern} % Job title
    {Sony Interactive Entertainment} % Organization
    {React Native, Redux, Python, Jenkins} % Location
    {Jan 2022 - Apr 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented checkout page UI elements based on design specifications using \boldstyle{React Native} and \boldstyle{Redux} to support the 2022 PlayStation Plus Subscription release.}
        % \item {Addressed several critical state management React/Redux bugs during time-sensitive sprints}
        \item {Automated E2E frontend regression tests in \boldstyle{Python} for 20+ checkout flows.} 
        \item {Achieved \boldstyle{first prize} in global hackathon with a team by creating a React Native calendar app for the PS5.}
      \end{cvitems}
    }

%---------------------------------------------------------
  % \cventry
  %   {Firmware Developer} % Job title
  %   {\href{https://www.uwmidsun.com/}{Midnight Sun} - University of Waterloo} % Organization
  %   {C, FreeRTOS, Python} % Location
  %   {Nov. 2021 - Present} % Date(s)
  %   {
  %     \begin{cvitems} % Description(s) of tasks/responsibilities
  %       \item {Migrated build system from GNU Make to Python Scons, improving extensibility of linting, formatting, and project setup.}
  %       \item {Ensured continuous voltage during pedal board operation of solar car by writing unit tests in C.}
  %     \end{cvitems}
  %   }

%---------------------------------------------------------
  \cventry
    {Full Stack Software Developer Intern} % Job title
    {\href{https://dreamschools.com/}{Dreamschools}} % Organization
    {React, Express, PostgreSQL, Stripe} % Location
    {May 2021 - Aug 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Addressed slow \boldstyle{Stripe} API calls by parallelizing/batching requests, improving load times by up to 10x.}
        \item {Developed complete messaging system and chat page using \boldstyle{React}, \boldstyle{Express} and \boldstyle{PostgreSQL} to provide SMS and email communication between clients.}
        \item {Overhauled checkout process by redesigning layout and supporting additional payment methods.}
      \end{cvitems}
    }
\end{cventries}
