%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Group Project} % Job title
    {\href{https://frankljin.github.io/hexle/}{Hexle - \underline{Game}} - \href{https://github.com/frankljin/hexle/}{\underline{Github}}} % Organization
    {TypeScript, React, CSS} % Location
    {Feb. - Mar. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Contributed to hex code guessing game with returning users from over 40 countries worldwide.}
        \item {Refactored initial code and React state management to improve maintainability and readability.}
        \item {Enhanced UI across devices by using responsive CSS and implementing a "side-by-side" colour comparison feature.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Midnight Sun Solar Car Strategy Team} % Job title
    {\href{https://github.com/uw-midsun/telemetry_xiv}{Midnight Sun Driver Dashboard - \underline{Github}}} % Organization
    {Flutter, Dart, Python} % Location
    {Apr. - Sep. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built digital dashboard for Midnight Sun's solar vehicle, including speedometer, battery life, target speed, and more.}
        \item {Performed CAN integration testing using mock CAN messages and Python driver code.}
        \item {Effectively used Flutter animations to direct driver attention when appropriate.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Personal Project} % Job title
    {\href{https://github.com/danielq987/superghost-explorer}{Solving SuperGhost - \underline{Github}}} % Organization
    {ExpressJS, Socket.io, PostgreSQL, Python} % Location
    {Oct. 2020 - Jan. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Solved word game 'SuperGhost' algorithmically by constructing 400,000-node directed graph.}
        \item {Created a prototype for real-time multiplayer SuperGhost using Javascript and Socket.io.}
        \item {Developed a backend server and database to support shareable game codes and game rooms.}
      \end{cvitems}
    }


\end{cventries}
